Forecasting the old-age dependency ratio to determine a sustainable pension age

### 2020-09-20 PensionAge.Rmd
Added reproducibility statement and cleaned up references

This is consistent with the Australian Intergenerational Reports [@IGR02; @IGR07; @Swan2010] that explored the extent to which existing age-related policies would affect the burden of future working generations. To date, the Australian government has addressed the problem through a variety of approaches including modifications to compulsory superannuation policies, instigating work incentives for older people, and increasing the pension age (defined as the age at which eligible residents can access the age pension for the first time). In 2009, the federal government announced an increase in pension age from 65 to 67 by 2023 [@Nielson2010]. In May 2014, the Federal Treasurer proposed a further increase in the pension age to 70 by 2035. This new proposal is in line with the recommendations from the @PC13 and the @NCOA2014. We investigate the effect of these changes in the pension age on the forecasts of the OADR.

@@

>>>>

This is consistent with the Australian Intergenerational Reports [@IGR02; @IGR07; @Swan2010] that explored the extent to which existing age-related policies would affect the burden of future working generations. To date, the Australian government has addressed the problem through a variety of approaches including modifications to compulsory superannuation policies, instigating work incentives for older people, and increasing the pension age (defined as the age at which eligible residents can access the age pension for the first time). In 2009, the federal government announced an increase in pension age from 65 to 67 by 2023 [@Nielson2010]. In May 2014, the Federal Treasurer proposed a further increase in the pension age to 70 by 2035, in line with the recommendations from the @PC13. We investigate the effect of these changes in the pension age on the forecasts of the OADR.

@@

## Reproducibility {-}

The data and code to fully reproduce our results is available at [`https://github.com/robjhyndman/PensionAge`](https://github.com/robjhyndman/PensionAge). We used R [@RCore], along with the drake [@Rdrake], tidyverse [@Rtidyverse], demography [@Rdemography] and forecast [@Rforecast] packages.
